### 2025-09-23 paper/sec/evaluation.tex
[update] result section, add table with results

\subsection{Results}
In this section, we present the experimental results.
Overall, the system produced a valid fluid expression in 74.9\% of the cases (S.D. 3\%).
Figure~\ref{fig:success_rate_by_category} illustrates the success rate for each category.

@@

\subsection{Negative Cases}
\label{subsec:negative-cases}

>>>>

\subsection{Results}

\begin{table}[h!]
    \scriptsize

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & 74   & 3 & 77.4 & 2 \\
            Data Retrieval & 76   & 3 & 77.4 & 2 \\
            Difference     & 80   & 3 & 77.4 & 2 \\
            Min/max        & 50   & 3 & 77.4 & 2 \\
            Rank           & 44   & 3 & 77.4 & 2 \\
            Total          & 33   & 3 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{gpt4o}} & \multicolumn{2}{c}{\textbf{gpt5}} \\
            & \textbf{Success Rate} & \textbf{SD} & \textbf{Success Rate} & \textbf{SD} \\
            \hline
            Comparison     & -- & -- & -- & -- \\
            Data Retrieval & -- & -- & -- & -- \\
            Difference     & -- & -- & -- & -- \\
            Min/max        & -- & -- & -- & -- \\
            Rank           & -- & -- & -- & -- \\
            Total          & -- & -- & -- & -- \\
            Overall        & -- & -- & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Comparison of success rates (with standard deviation) between \textbf{gpt4o} and \textbf{gpt5} across different task categories, reported with and without the use of target-values.}
    \label{tab:results_combined}
\end{table}

In this section, we report the experimental results.
Table \ref{tab:results_combined} summarizes the performance of \textit{gpt4o} and the most recent OpenAI model, \textit{gpt5}, under two different settings: with target-value sharing enabled and without target-value sharing.
Overall, the system produced a valid fluid expression in 74.9\% of the cases (S.D. 3\%).

Figure~\ref{fig:success_rate_by_category} illustrates the success rate for each category, both with and without target-value sharing.
The results show that providing the target value is crucial for achieving a high success rate.
Moreover, the \InterpretationAgent generates a correct expression in approximately XX\% of the cases.

@@

In addition to evaluating performance when the target expression is provided, we also assessed the model’s ability to produce a
correct expression when no reference string was given.
On the SciGen dataset, the model achieved a 74.9\% success rate when provided with the target string.
Without the target string, performance decreased moderately to 39.4\%, indicating that the model retains substantial
ability to reconstruct valid solutions even without explicit guidance

\subsection{Problematic Cases}
\label{subsec:problematic-cases}
